### 2016-11-03 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
Eds

Fig1A <- ggplot(temp,aes(x = Agemonths,y = RTL,group = BirdID,col=factor(BirdID)))+
  geom_point(alpha = 1,col='grey')+
geom_line(col = 'darkgrey',alpha = 0.2)+
  xlab('Age (years)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none')+
  geom_smooth(col = 'black',fill = 'black',lwd = 0.5,aes(group = NULL),method = 'lm',formula = y~log(x))+
  annotate('text',x = 0,y = 3,label = 'A')

@@

Fig1B <- ggplot(temp,
       aes(x = RTL,
           y = RTL1)) +
  ylab('Adult RTL') + 
  xlab('juvenile RTL') +
    xlim(c(0,3))+
  ylim(c(0,3))+
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c('none'),
        legend.title = element_text(size = 12),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
    geom_point(col = 'grey')+
  geom_abline(slope = 1,intercept = 0,lty = 2)+
  annotate('text',x = 0,y = 3,label = 'B')

Fig1C <- ggplot(ddL,aes(col=Group,fill = Group,y = ..scaled..,x = DeltaRTL))+
    geom_density(alpha = 0.2)+
  theme_classic()+
  ylab ('Scaled density')+
  xlab(expression(Delta*'RTL'))+
    theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'none',
        legend.title = element_blank(),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
  scale_colour_manual(values = c('darkgrey','gold'))+
  scale_fill_manual(values = c('darkgrey','gold'))+
  geom_vline(xintercept = 0,lty = 2)+
  annotate('text',x = -2,y = 1,label = 'C')

@@

Fig1D <- ggplot(temp,aes(y = DeltaRTL,x = TimeDiff))+
    geom_point(col = 'grey')+
  theme_classic()+ 
  xlab ('Follow up time (years)')+
  ylab(expression(Delta*'RTL'))+
  ylim(c(-2,2))+
    theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c('none'),
        legend.title = element_blank(),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
    geom_abline(slope = 0,intercept = 0,lty = 2)+
  annotate('text',x = 0,y = 2,label = 'D')

@@

Fig2A <- ggplot(temp,aes(x = Agemonths,y = RTL,col = Cohort))+
  xlab('Age (months)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'))+
  geom_smooth(method = 'lm',formula = y~log(x),se = F)+
  annotate('text',x = 0,y = 1.3,label = 'A')

Fig2B <- ggplot(temp,aes(x = Agemonths,y = RTL,col = Cohort))+
  xlab('Age (months)') +
  geom_point()+
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'))+
  geom_smooth(se = F)+
  annotate('text',x = 0,y = 1.4,label = 'B')

@@

Fig3A <- forestplot(table2)+
  annotate('text',x = 0.6,y = 0.25,label = 'A')+
  theme(axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'))

  Fig3B <- ggplot(temp,
       aes(x = Agemonths,
           y = RTL,
           col = Sex)) +
  geom_point()+
  ylab('RTL') + 
  xlab('Age (months)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none') +
  stat_smooth(method = 'lm',formula = y~log(x))+
  annotate('text',x = 1,y = 2.5,label = 'B')

Fig3C <- ggplot(temp,
       aes(x = Tarsus,
           y = RTL,
           col = Sex)) +
  geom_point()+
  ylab('RTL') + 
  xlab('Tarsus length (mm)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none') +
  stat_smooth(method = 'lm')+
  annotate('text',x = 17,y = 2.5,label = 'C')

Fig3D <- ggplot(temp,
       aes(
           y = RTL,
           x=Insect)) +
    ylab('RTL') + 
  xlab('Insect abundance') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none') +
  geom_boxplot(aes(group = Insect),outlier.shape = NA)+
   stat_smooth(method = 'lm',col = 'darkgrey')+
  annotate('text',x = 2.5,y = 2.5,label = 'D')

Fig3E <- ggplot(temp,
       aes(
           y = RTL,
           x=Density)) +
    ylab('RTL') + 
  xlab('Density') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none') +
  geom_boxplot(aes(group = Insect),outlier.shape = NA)+
   stat_smooth(method = 'lm',col = 'darkgrey')+
  annotate('text',x = 270,y = 2.5,label = 'E')

@@

plot(tapply(dd3$DeltaRTLF,dd3$TimeDiff,mean))

ggplot(dd,aes(col = Whodunnit,y = RTL,x = factor(LayYear)))+
geom_boxplot()

>>>>

Fig1A <- ggplot(temp,aes(x = Agemonths,y = RTL,group = BirdID,col=factor(BirdID)))+
  geom_point(alpha = 1,col='grey')+
geom_line(col = 'darkgrey',alpha = 0.2)+
  xlab('Age (years)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none')+
  geom_smooth(col = 'black',fill = 'black',lwd = 0.5,aes(group = NULL),method = 'lm',formula = y~log(x))
  annotate('text',x = 0,y = 3,label = 'A')

@@

Fig1B <- ggplot(temp,
       aes(x = RTL,
           y = RTL1)) +
  ylab(expression('RTL ('*italic(t)*' + 1)')) + 
  xlab(expression('RTL ('*italic(t)*')')) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c('none'),
        legend.title = element_text(size = 12),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
    geom_point(col = 'grey')+
  geom_abline(slope = 1,intercept = 0,lty = 2)
  annotate('text',x = 0,y = 3,label = 'B')

Fig1C <- ggplot(ddL,aes(col=Group,fill = Group,y = ..scaled..,x = DeltaRTL))+
    geom_density(alpha = 0.2)+
  theme_classic()+
  ylab ('Scaled density')+
  xlab(expression(Delta*'RTL'))+
    theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'none',
        legend.title = element_blank(),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
  scale_colour_manual(values = c('darkgrey','gold'))+
  scale_fill_manual(values = c('darkgrey','gold'))+
  geom_vline(xintercept = 0,lty = 2)
  annotate('text',x = -2,y = 1,label = 'C')

@@

Fig1D <- ggplot(temp,aes(y = DeltaRTL,x = TimeDiff))+
    geom_point(col = 'grey')+
  theme_classic()+ 
  xlab ('Follow up time (years)')+
  ylab(expression(Delta*'RTL'))+
    theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c('none'),
        legend.title = element_blank(),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
    geom_abline(slope = 0,intercept = 0,lty = 2)
  annotate('text',x = 0,y = 2,label = 'D')

@@

Fig2A <- ggplot(temp,aes(x = Agemonths,y = RTL,col = Cohort))+
  xlab('Age (months)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'))+
  geom_smooth(method = 'lm',formula = y~log(x),se = F)
  annotate('text',x = 0,y = 1.3,label = 'A')

temp2 <- ddply(temp,
               .(Agemonths,Cohort),
               summarise,
               MedianRTL = mean(RTL))  %>%
  subset(Agemonths < 20)

Fig2B <- ggplot(temp2,aes(x = Agemonths,y = MedianRTL,col = Cohort))+
  xlab('Age (months)') +
  geom_line()+
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'))
  annotate('text',x = 0,y = 1.4,label = 'B')

@@

Fig3A <- forestplot(table2)+
  annotate('text',x = 0.6,y = 0.05,label = 'A')+
  theme(axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'))

  Fig3B <- ggplot(temp,
       aes(x = Agemonths,
           y = RTL,
           col = Sex)) +
  geom_point()+
  ylab('RTL') + 
  xlab('Age (months)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none') +
  stat_smooth(method = 'lm',formula = y~log(x))
  annotate('text',x = 1,y = 2.5,label = 'B')

Fig3C <- ggplot(temp,
       aes(x = Tarsus,
           y = RTL,
           col = Sex)) +
  geom_point()+
  ylab('RTL') + 
  xlab('Tarsus length (mm)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none') +
  stat_smooth(method = 'lm')
  annotate('text',x = 17,y = 2.5,label = 'C')

Fig3D <- ggplot(temp,
       aes(
           y = RTL,
           x=Insect)) +
    ylab('RTL') + 
  xlab('Insect abundance') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none') +
  geom_boxplot(aes(group = Insect),outlier.shape = NA)+
   stat_smooth(method = 'lm',col = 'darkgrey')
  annotate('text',x = 2.5,y = 2.5,label = 'D')

Fig3E <- ggplot(temp,
       aes(
           y = RTL,
           x=Density)) +
    ylab('RTL') + 
  xlab('Density') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none') +
  geom_boxplot(aes(group = Insect),outlier.shape = NA)+
   stat_smooth(method = 'lm',col = 'darkgrey')
  annotate('text',x = 270,y = 2.5,label = 'E')

@@
